---
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
library(readxl)
library(lubridate)
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(zoo)
library(kableExtra)

##install.packages("psych")
library(psych)
```

```{r}
EU_price<-read.csv(file="./Data/World_NG_Price.csv")
EU_price$Date<-as.Date(EU_price$Date)
#EU_price

EU_GDP<-read.csv(file="./Data/EU_GDP_Normalized.csv")
EU_GDP
EU_GDP<-EU_GDP %>%
  rename(GDP = GDP1) %>%
  rename(Date = DATE)
EU_GDP$Date <- as.Date(EU_GDP$Date)

Consumption <- read_excel("./Data/Natual Gas Consumption.xlsx")
Consumption <- Consumption[,1:2]
Consumption$Date <- as.Date(paste(Consumption$Date,"-01",sep=""))
Consumption <- na.omit(Consumption)
<<<<<<< HEAD

=======
>>>>>>> 6ad2dcf6109bc26abf267e2d242a30517eacf77b
Import <- read_excel("./Data/Natual Gas Imports.xlsx")
Import <- Import[,1:4]
Import$Date <- as.Date(paste(Import$Date,"-01",sep=""))
Import <- na.omit(Import)
```

```{r}
EU_price<-EU_price%>%
  rename( Price=PNGASEUUSDM ) 
#tail(EU_price)
```
#According to IEA, the EU imported 155 bcm of natural gas from Russia in 2021, accounting for around 45% of the EU’s total gas imports and 40% of its total gas consumption. Considering the EU countries plan to reduce or even embargo the natural gas imports from Russia after the Russian invasion of Ukraine, the natural gas price in Europe is expected to experience the most direct impact.

```{r}
ts_EU_price <- ts(EU_price$Price,frequency=12,start=c(1990,01))
autoplot(ts_EU_price,main="Figure 1. Historical EU Natural Gas Price")+ylab("Natural Gas Price ($/MMBtu) ")
```

```{r}
ts_EU_GDP <- ts(EU_GDP$GDP,frequency=12,start=c(1960,03))
#plot(ts_EU_GDP)
```

```{r}
ts_consumption <- ts(Consumption$Consumption,frequency=12,start=c(2014,01))
#plot(ts_consumption)
#ts_consumption %>% mstl() %>%
#autoplot()
```

```{r}
ts_import1 <- ts(Import$Import1,frequency=12,start=c(2014,01))
ts_import2 <- ts(Import$Import2,frequency=12,start=c(2014,01))
ts_import3 <- ts(Import$Import3,frequency=12,start=c(2014,01))
#ts_import1 %>% mstl() %>%
#plot(ts_EU_import1)
```


```{r}
library(trend)
pettittTest<-pettitt.test(ts_EU_price)
print(pettittTest)
```
#p value is really small, reject the null, so there is a change in trend.
#The point of change is 12*14+9=177, so the change in trend happens in 2004.09.01.

```{r}
ts_EU_price %>% mstl() %>%
autoplot()
```
#Based on the ACF and PACF plots of the natural gas price data, we found no seasonality and decided not to include seasonality in our following analysis.

```{r}
ts_EU_price_shorten_200409_202203 <- ts(EU_price$Price[177:387],frequency=12,start=c(2004,09))
#plot(ts_EU_price_shorten_200409_202203)
```

```{r}
pettittTest2<-pettitt.test(ts_EU_price_shorten_200409_202203)
print(pettittTest2)
```
#By using the pettitt.test function, we found two points of inflection in our historical natural gas price data, one in September 2004 and the other one in July 2014, which means that there is no significant change in the trend after 2014. Because Russia started mobilizing its troops near Ukraine at the beginning of 2022, we assume that the impact of Ukraine crisis happens starts in January 2022, causing tension that has already driven up the natural gas price.

```{r}
#ts_EU_price_shorten_201407_202203 <- ts(EU_price$Price[295:387],frequency=12,start=c(2014,07))
#plot(ts_EU_price_shorten_201407_202203)
```

```{r}
#ts_EU_price_shorten_201407_202203 %>% mstl() %>%
#autoplot()
```

```{r}
df_cor<-cbind(EU_price$Price[295:372],EU_GDP$GDP,Consumption$Consumption,Import$Import1)
df_cor<-cor(df_cor)
row.names(df_cor) <- c("Price", "GDP", "Consumption", "Import")
colnames(df_cor) <- c("Price", "GDP", "Consumption", "Import")
table_1 <- kable(df_cor,"pipe", caption = "Table.1 Variable Correlations")
table_1
```
#To understand the degree of this impact, we collected the historical monthly natural gas price and the monthly normalized GDP in Europe from Federal Reserve Banks of St.Louis’ website, and the monthly natural gas consumption and import in the EU from the Eurostat data browser. Through exploring the correlations between natural gas price and the other factors, we found that while all variables have weak correlations, GDP and imports have much stronger correlations than consumptions (table_1). While GDP is positively correlated with the natural gas price, import is negatively correlated. Therefore, we decided to use GDP and natural gas imports as exogenous variables for our ARIMA model. Considering GDP has a positive correlation of 0.05 with import, we will include both variables in one of our models too.

```{r table}
data <- cbind(EU_price$Price[295:372],EU_GDP$GDP,Consumption$Consumption,Import$Import1)
colnames(data) <- c("Price ($/MMBtu)", "GDP(Normalized)", "Consumption(Million Cubic Metres)", "Import(Million Cubic Metres)")
table_2 <- kable(head(data,10),"pipe", caption = "Table 2. First ten rows of data")
summary <- describe(data)
summary <- signif(summary, digits=3)
summary$source <- c("FRED", "FRED", "Eurostat", "Eurostat")
summary <- summary[,-1]
table_3 <- kable(summary,"pipe", caption = "Table 3. Data Descriptions")
table_2
table_3
```

```{r}
ts_EU_price_shorten_201407_202012 <- ts(EU_price$Price[295:372],frequency=12,start=c(2014,07))
ts_EU_price_shorten_201407_202012 %>% mstl() %>%
autoplot()
SARIMA_autofit <- auto.arima(ts_EU_price_shorten_201407_202012)
SARIMA_autofit
checkresiduals(SARIMA_autofit)
ts_EU_price_shorten_201407_202012
```
ARIMA(0,1,0) = random walk:  If the series Y is not stationary, the simplest possible model for it is a random walk model. This can be considered as a limiting case of an AR(1) model in which the autoregressive coefficient is equal to 1, i.e., a series with infinitely slow mean reversion.  The prediction equation for this model can be written as:

Ŷt  - Yt-1   =  μ

or equivalently

Ŷt  =   μ + Yt-1

...where the constant term is the average period-to-period change (i.e. the long-term drift) in Y.  This model could be fitted as a no-intercept regression model in which the first difference of Y is the dependent variable.  Since it includes (only) a nonseasonal difference and a constant term, it is classified as an "ARIMA(0,1,0) model with constant." The random-walk-without-drift model would be an ARIMA(0,1,0) model without constant

```{r}
par(mfrow=c(1,2))  #place plot side by side
Acf(ts_EU_price_shorten_201407_202203,lag.max=40,main="ACF of Price")
Pacf(ts_EU_price_shorten_201407_202203,lag.max=40,main="PACF of Price")
```

```{r}
print("Results for ADF test on EU NG Price data")
print(adf.test(ts_EU_price_shorten_201407_202203, alternative = "stationary"))
```

```{r}
#Because we know the time series contain a stochastic trend, we need to difference it first and use the ACF and PACF of differenced series to determine the parameters. 

diff_EU_price=diff(x=EU_price$Price[295:387],lag=1,differences=1)
ts_diff_EU_price <- ts(diff_EU_price,frequency=12,start=c(2014,7), end=c(2022,03))
autoplot(ts_diff_EU_price)+ylab("differenced EU Natural Gas Price ($/MMBtu)")

par(mfrow=c(1,2))
Acf(ts_diff_EU_price,lag.max=60)
Pacf(ts_diff_EU_price,lag.max=60)
```
  The ADF test indicates that the original series contains a unit root (i.e. there is a stochastic trend)(p>0.99). After removing the trend by differencing, the detrended series doesn’t show a constant pattern within each year. Instead, it looks like a white noise with mean around zero and fluctuating up and down randomly over time. This situation indicates that the original time series doesn’t contain a seasonality component. 
  Neither ACF or PACF of the differenced series show significant values, which could be caused by the superimposing of autoregression and moving average terms.

```{r NG price trimming}
n_for=3
ts_EU_price_train<-subset(ts_EU_price_shorten_201407_202203,end=length(ts_EU_price_shorten_201407_202203)-n_for)
ts_EU_price_test<-subset(ts_EU_price_shorten_201407_202203,start=length(ts_EU_price_shorten_201407_202203)-n_for)

```
From the historical NG price data, we observed a huge increase started from January 2021. Because we want to compare models performance under disruptions, we purposely include this increasing trend in the training set. Thus, our training set includes data from July 2014 to December, while our test set include the data from January to March 2022. 
```{r GDP trimming}
ts_EU_GDP_201407_202203 <- ts(EU_GDP$GDP[640:732],frequency=12,start=c(2014,07))
ts_EU_GDP_train<-subset(ts_EU_GDP_201407_202203,end=length(ts_EU_GDP_201407_202203)-n_for)
ts_EU_GDP_test<-subset(ts_EU_GDP_201407_202203,start=length(ts_EU_GDP_201407_202203)-n_for)
ts_EU_GDP_train %>% mstl() %>%
autoplot()
ts_EU_GDP1_201407_202301<-ts(EU_GDP$GDP[640:742],frequency=12,start=c(2014,07))
ts_EU_GDP2_201407_202301<-ts(EU_GDP$GDP2[640:742],frequency=12,start=c(2014,07))
ts_EU_GDP3_201407_202301<-ts(EU_GDP$GDP3[640:742],frequency=12,start=c(2014,07))
```


```{r}
ts_EU_GDP2_201407_202203 <- ts(EU_GDP$GDP2[640:732],frequency=12,start=c(2014,07))
ts_EU_GDP_train2<-subset(ts_EU_GDP2_201407_202203,end=length(ts_EU_GDP2_201407_202203)-n_for)
ts_EU_GDP_test2<-subset(ts_EU_GDP2_201407_202203,start=length(ts_EU_GDP2_201407_202203)-n_for)
```

```{r}
ts_EU_GDP3_201407_202203 <- ts(EU_GDP$GDP3[640:732],frequency=12,start=c(2014,07))
ts_EU_GDP_train3<-subset(ts_EU_GDP3_201407_202203,end=length(ts_EU_GDP3_201407_202203)-n_for)
ts_EU_GDP_test3<-subset(ts_EU_GDP3_201407_202203,start=length(ts_EU_GDP3_201407_202203)-n_for)
```

```{r GDP 2022-2023 data trimming}
ts_EU_GDP1_202203_202301 <- ts(EU_GDP$GDP[745:755],frequency=12,start=c(2022,03))

ts_EU_GDP2_202203_202301 <- ts(EU_GDP$GDP2[745:755],frequency=12,start=c(2022,03))

ts_EU_GDP3_202203_202301 <- ts(EU_GDP$GDP3[745:755],frequency=12,start=c(2022,03))
```

```{r Import trimming}
ts_EU_import1_201407_202212<-ts(Import$Import1[7:108],frequency=12,start=c(2014,07))
ts_EU_import2_201407_202212<-ts(Import$Import2[7:108],frequency=12,start=c(2014,07))
ts_EU_import3_201407_202212<-ts(Import$Import3[7:108],frequency=12,start=c(2014,07))
ts_EU_import_201407_202203<-ts(Import$Import3[7:99],frequency=12,start=c(2014,07))
ts_EU_import_train<-subset(ts_EU_import_201407_202203,end=length(ts_EU_import_201407_202203)-n_for)
ts_EU_import_test<-subset(ts_EU_import_201407_202203,start=length(ts_EU_import_201407_202203)-n_for)
```
In order to accurately forecast the natural gas price in 2022, we created three scenarios for each of the two exogenous variables. For GDP growth in the EU in 2022, the EU Economic and Social committee estimated a growth of 4% (GDP_scenario_1) before the Russian invasion of Ukraine, and dropped its estimation to 3% (GDP_scenario_2) after the invasion. Yet, some investment banks like Credit Suisse predicted an annual GDP growth of only 1% (GDP_scenario_3) due to this invasion. While the level of sanctions on natural gas imports from Russia is still under debate in different countries in the EU, we expect the total natural gas import in the EU would decrease about 20% (Import_scenario_2) if there is a complete embargo on Russian imports. If the EU countries failed to embargo Russia, a 10% decrease (Import_scenario_2) in natural gas imports is expected with some sanctions on Russia, and only a 5% decrease (Import_scenario_3) if the sanctions are not strictly implemented.

Graphs below show the forecasted price from fitted model regarding the training set compared to the observed ones.
```{r}
#Neural Network Test
NN_fit <- nnetar(ts_EU_price_train)
NN_for <- forecast::forecast(NN_fit, h=3)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for, series="Neural Network",PI=FALSE)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```

```{r NN+Import Fit}
NN_fit_withImport <- nnetar(ts_EU_price_train,xreg=ts_EU_import_train)

NN_for_withImport <- forecast::forecast(NN_fit_withImport,xreg=ts_EU_import_test,h=3)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_withImport, series="Neural Network+Import",PI=FALSE)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
```{r}
##NN+GDP
NN_fit_withGDP <- nnetar(ts_EU_price_train,xreg=ts_EU_GDP_train)

NN_for_withGDP <- forecast::forecast(NN_fit_withImport,xreg=ts_EU_GDP_test,h=3)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_withGDP, series="Neural Network+GDP",PI=FALSE,showgap=F)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
```{r}
##NN+GDP
NN_fit_withGDPandImport <- nnetar(ts_EU_price_train,xreg=cbind(ts_EU_GDP_train,ts_EU_import_train))

NN_for_withGDPandImport <- forecast::forecast(NN_fit_withGDPandImport,xreg=cbind(ts_EU_GDP_test,ts_EU_import_test),h=3)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_withGDPandImport, series="Neural Network+GDP+Import",PI=FALSE,showgap=F)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```


```{r}
#ETS+STL
#Forecasts of `stl` objects can be obtained using function `stlf()`. Forecast will be obtained by applying a non-seasonal exponential smoothing model to the seasonally adjusted data and re-seasonalizing using the last year of the seasonal component (for all seasonal components).
ETS_fit <-  stlf(ts_EU_price_train,h=3)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ETS_fit, series="STL + ETS",PI=FALSE,showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")
```
```{r}
# TBATS
TBATS_fit <- tbats(ts_EU_price_train)

TBATS_for <- forecast::forecast(TBATS_fit, h=3)

#Plot foresting results
autoplot(TBATS_for) +
  ylab("EU NG Price") 

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(TBATS_for, series="TBATS",PI=FALSE,showgap=F)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```

```{r Auto Arima Fit}
#ARIMA autofit
ARIMA_Four_fit <- auto.arima(ts_EU_price_train, 
                             seasonal=FALSE, 
                             lambda=0
                             )
checkresiduals(ARIMA_Four_fit)
ARIMA_Four_for <- forecast::forecast(ARIMA_Four_fit,h=3
                           ) 

#Plot foresting results
autoplot(ARIMA_Four_for) + ylab("EU NG Price")

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_Four_for, series="ARIMA",PI=FALSE,showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")
```
The residual from the ARIMA(1,0,4) appears to be white noise with mean around zero and no clear trend observed. THe residuals are normally distributed, and all ACF are within the intervals (i.e. insignificant).

```{r ARIMA+GDP}
#Fit Arima model with GDP as regressor
ARIMA_Four_fit_withGDP <- auto.arima(ts_EU_price_train,
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=ts_EU_GDP_train
                             )
#Forecast test based on fitted model
ARIMA_Four_for_withGDP <- forecast::forecast(ARIMA_Four_fit_withGDP,
                           xreg=ts_EU_GDP_test,
                           h=3
                           ) 

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_Four_for_withGDP, series="ARIMA+GDP",PI=FALSE,showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")
```

```{r ARIMA+Import}
#Manually fit Arima model with import as regressor
#auto-fit gives poor result ARIMA (0,0,0)
ARIMA_Four_fit_withImport_false<-auto.arima(ts_EU_price_train,xreg=ts_EU_import_train)
checkresiduals(ARIMA_Four_fit_withImport_false)

ARIMA_Four_fit_withImport <- Arima(ts_EU_price_train,order=c(0,1,1),include.drift=TRUE,xreg=ts_EU_import_train
                             )
#Forecast test based on fitted model
ARIMA_Four_for_withImport <- forecast::forecast(ARIMA_Four_fit_withImport,
                           xreg=ts_EU_import_test,
                           h=3
                           ) 
checkresiduals(ARIMA_Four_fit_withImport)
#Plot foresting results
autoplot(ARIMA_Four_for_withImport) + ylab("EU Natural Gas Price ($/MMBtu)")

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_Four_for_withImport, series="ARIMA+Import",PI=FALSE,showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")
```
```{r}
#ARIMA with both Import and GDP
auto_ARIMA_fit_withImportandGDP<-auto.arima(ts_EU_price_train,xreg=cbind(ts_EU_import_train,ts_EU_GDP_train))
checkresiduals(auto_ARIMA_fit_withImportandGDP)

#Manually fit
ARIMA_fit_withImportandGDP <- Arima(ts_EU_price_train,order=c(0,1,1),include.drift=TRUE,xreg=cbind(ts_EU_import_train,ts_EU_GDP_train))
checkresiduals(ARIMA_fit_withImportandGDP)

ARIMA_for_withImportandGDP <- forecast::forecast(ARIMA_fit_withImportandGDP,
                           xreg=cbind(ts_EU_import_test,ts_EU_GDP_test),
                           h=3
                           ) 
checkresiduals(ARIMA_for_withImportandGDP)
#Plot foresting results
autoplot(ARIMA_for_withImportandGDP) + ylab("EU Natural Gas Price ($/MMBtu)")

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_for_withImportandGDP, series="ARIMA+GDP+Import",PI=FALSE,showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")
```
```{r}
#Model 1: STL + ETS
ETS_scores <- accuracy(ETS_fit$mean,ts_EU_price_test)  

#Model 2: ARIMA
ARIMA_scores <- accuracy(ARIMA_Four_for$mean,ts_EU_price_test)

# Model 3:  TBATS 
TBATS_scores <- accuracy(TBATS_for$mean,ts_EU_price_test)

# Model 4:  Neural Network 
NN_scores <- accuracy(NN_for$mean,ts_EU_price_test)

#Model 5: ARIMA+GDP1
ARIMA_GDP1_scores <- accuracy(ARIMA_Four_for_withGDP$mean,ts_EU_price_test)

#Model 6: ARIMA+Import1
ARIMA_Import1_scores <- accuracy(ARIMA_Four_for_withImport$mean,ts_EU_price_test) 

#Model 7:NN+Import1
NN_withImport_scores <- accuracy(NN_for_withImport$mean,ts_EU_price_test) 

#Model 8:NN+GDP1
NN_withGPD_scores <- accuracy(NN_for_withGDP$mean,ts_EU_price_test) 

#Model 9:NN+GDP+Import
NN_withImportandGDP_scores <- accuracy(NN_for_withGDPandImport$mean,ts_EU_price_test) 

#Model 10:ARIMA+GDP+Import
ARIMA_withGDPandImport_scores <- accuracy(ARIMA_for_withImportandGDP$mean,ts_EU_price_test) 
```

```{r}
scores <- as.data.frame(
  rbind(ETS_scores, ARIMA_scores, TBATS_scores, NN_scores,ARIMA_GDP1_scores,ARIMA_Import1_scores,ARIMA_withGDPandImport_scores,NN_withImport_scores,NN_withGPD_scores,NN_withImportandGDP_scores)
  )
row.names(scores) <- c("STL+ETS", "ARIMA","TBATS","NN","ARIMA+GDP","ARIMA+Import","ARIMA+Import+GDP","NN+Import","NN+GDP","NN+GDP+Import")

#choose model with lowest RMSE
best_model_index <- which.min(scores[,"RMSE"])
cat("The best model by RMSE is:", row.names(scores[best_model_index,]))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
kbl(scores, 
      caption = "Forecast Accuracy for EU NG Price",
      digits = array(5,ncol(scores))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  #highlight model with lowest RMSE
  kable_styling(latex_options="striped", stripe_index = which.min(scores[,"RMSE"]))
```
<<<<<<< HEAD
#According to the table, the model with the lowest RMSE score is NN purely dependent on historical NG price, the second best model is STL+ETS, followed by ARIMA+Import+GDP. Thus, we choose NN as the model to fit the forecast for 2022. It is noteworthy that our choice of test set is uncommon, because we expect NG prices follow different trend after Ukraine crisis, so this only applies to our data set that undergoes a huge increase and lots of fluctuations. 
#The effect of exogenous variables depends on different models. For example, among all ARIMA models, the best one is ARIMA with both GDP and Import, but among all NN models, the NN without any exogenous variable.
=======
  According to the table, the model with the lowest RMSE score is NN purely dependent on historical NG price, the second best model is STL+ETS, followed by ARIMA+Import+GDP. Thus, we choose NN as the model to fit the forecast for 2022. It is noteworthy that our choice of test set is uncommon, because we expect NG prices follow different trend after Ukraine crisis, so this only applies to our data set that undergoes a huge increase and lots of fluctuations. 
  The effect of exogenous variables depends on different models. For example, among all ARIMA models, the best one is ARIM with both GDP and Import, but among all NN models, the NN without any exogenous variable.
>>>>>>> 6ad2dcf6109bc26abf267e2d242a30517eacf77b

```{r}
ts_forplot<-ts(ts_EU_price_shorten_201407_202203[69:93],frequency=12, start=c(2020,03))
autoplot(ts_forplot,main="Comparison between Observed Data and Forecasted Values") +
  autolayer(ETS_fit, PI=FALSE, series="STL+ETS",showgap=F) +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA",showgap=F) +
  autolayer(TBATS_for,PI=FALSE, series="TBATS",showgap=F) +
  autolayer(NN_for,PI=FALSE, series="NN",showgap=F) +
  #autolayer(NN_for_withGDP,PI=FALSE, series="NN+GDP",showgap=F) +
  #autolayer(NN_for_withImport,PI=FALSE, series="NN+Import",showgap=F) +
  #autolayer(NN_for_withGDPandImport,PI=FALSE, series="NN+GDP+Import",showgap=F) +
  #autolayer(ARIMA_Four_for_withImport,PI=FALSE, series="ARIMA+Import",showgap=F) +
  #autolayer(ARIMA_for_withImportandGDP,PI=FALSE, series="ARIMA+GDP+Import",showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)") +
  guides(colour=guide_legend(title="Models"))
```
<<<<<<< HEAD
#To better analyze the differences between different models, forecasts without exogenous variables are plotted and analyzed separately below. This graph only shows comparison between observed data and the forecasts based on the NG historical price training set. TBATs performs well in following the trend observed recently, but it failed to integrate the fluctuations, thus receiving the highest RMSE score. NN and STL+ETS forecast the same price in January, while NN and ARIMA forecast the same price in March.
=======
  To better analyze the differences between different models, forecasts with exogenous variables are plotted and analyzed separately below. This graph only shows comparison between observed data and the forecasts based on the training set. TBATs performs well in following the trend observed recently, but it failed to integrate the fluctuations, thus receiving the highest RMSE score. NN and STL+ETS forecast the same price in January, while NN and ARIMA forecast the same price in March.
>>>>>>> 6ad2dcf6109bc26abf267e2d242a30517eacf77b
```{r}
autoplot(ts_forplot,main="Comparison between NN Forecasterd Values") +
  #autolayer(ETS_fit, PI=FALSE, series="STL+ETS",showgap=F) +
  #autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA",showgap=F) +
  #autolayer(TBATS_for,PI=FALSE, series="TBATS",showgap=F) +
  autolayer(NN_for,PI=FALSE, series="NN",showgap=F) +
  autolayer(NN_for_withGDP,PI=FALSE, series="NN+GDP",showgap=F) +
  autolayer(NN_for_withImport,PI=FALSE, series="NN+Import",showgap=F) +
  autolayer(NN_for_withGDPandImport,PI=FALSE, series="NN+GDP+Import",showgap=F) +
  #autolayer(ARIMA_Four_for_withImport,PI=FALSE, series="ARIMA+Import",showgap=F) +
  #autolayer(ARIMA_for_withImportandGDP,PI=FALSE, series="ARIMA+GDP+Import",showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)") +
  guides(colour=guide_legend(title="Models"))
```
  Among NN models results, both NN with import as a regressor and NN with both import and GDP forecast an increase in natural gas price in January 2022 and then a significant decrease in Feburary 2022, while NN and NN with GDP forecast a decrease in January. Overall, there is a significant overlap between NN+GDP+Import and NN+import forecasts, which indicates that import has a greater impact on the forecast results. Compared to the original NN, the integration of import data increases the fluctuation of the forecast results, while GDP only brings up the level of forecast slightly and keeps the flucatation similar as before.
```{r}
autoplot(ts_forplot,main="Comparison between ARIMA Forecasterd Values") +
  #autolayer(ETS_fit, PI=FALSE, series="STL+ETS",showgap=F) +
  autolayer(ARIMA_Four_for, PI=FALSE, series="ARIMA",showgap=F) +
  #autolayer(TBATS_for,PI=FALSE, series="TBATS",showgap=F) +
  #autolayer(NN_for,PI=FALSE, series="NN",showgap=F) +
  #autolayer(NN_for_withGDP,PI=FALSE, series="NN+GDP",showgap=F) +
  #autolayer(NN_for_withImport,PI=FALSE, series="NN+Import",showgap=F) +
  #autolayer(NN_for_withGDPandImport,PI=FALSE, series="NN+GDP+Import",showgap=F) +
  autolayer(ARIMA_Four_for_withGDP,PI=FALSE, series="ARIMA+GDP",showgap=F)+
  autolayer(ARIMA_Four_for_withImport,PI=FALSE, series="ARIMA+Import",showgap=F) +
  autolayer(ARIMA_for_withImportandGDP,PI=FALSE, series="ARIMA+GDP+Import",showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)") +
  guides(colour=guide_legend(title="Models"))
```
  Among ARIMA models results, all four models shows a increase trend in January, and then a decrease trend in Feburary. Compared to the ARIMA that only depends on NG price, GDP as a regressor doesn't change the overall trend of the forecast, while import shows a larger impact on the forecast result When both GDP and import data are added into the ARIMA model, the forecast almost overlaps with the one from ARIMA+import, which indicates that import has a greater impact onto the forecast result compared to GDP.

```{r}
#NN forecast until 2022.12
NN_fit_202212 <- nnetar(ts_EU_price_shorten_201407_202203)
NN_for_202212 <- forecast::forecast(NN_fit_202212, h=10)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_202212,showgap=F)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
  According to the NN model purely dependent on NG historical price, the forecast results show that EU NG price will flucturates a lot thorughout the year with an overall decreasing trend. The peak is forecasted to be in March 2022, and the price will falls back to 28 $/MMBtu at the end of the year. 


```{r}
#NN forecast in three GDP scenarios
NN_fit_withGDP_202212 <- nnetar(ts_EU_price_shorten_201407_202203,xreg=ts_EU_GDP_201407_202203)
#checkresiduals(NN_fit_withImport_202212)
#NN_for <- forecast(NN_fit, h=365) 
NN_for_withGDP1_202212 <- forecast::forecast(NN_fit_withGDP_202212,xreg=ts_EU_GDP1_202203_202301,
                           h=9)

NN_for_withGDP2_202212 <- forecast::forecast(NN_fit_withGDP_202212,xreg=ts_EU_GDP2_202203_202301,
                           h=9)

NN_for_withGDP3_202212 <- forecast::forecast(NN_fit_withGDP_202212,xreg=ts_EU_GDP3_202203_202301,
                           h=9)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_withGDP1_202212, series="20%",showgap=F)+
  autolayer(NN_for_withGDP2_202212, series="10%",showgap=F)+
  autolayer(NN_for_withGDP3_202212, series="5%",PI=FALSE,showgap=F)+
  guides(colour=guide_legend(title="Scenarios (GDP Increase)"))+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
  NN with GDP as a regressor shows a similar pattern compared to the original NN model, the peak is still forecasted to be happen at March 2022, but overall the integration of GDP drives up the level of the price forecast to 35 $/MMBtu at the end of the year. Three GDP scnearios don't lead to any significant effect on the forecast results.

```{r}
#NN forecast in three import scenarios
NN_fit_withImport_202212 <- nnetar(ts_EU_price_shorten_201407_202203,xreg=ts_import1[7:99])
#checkresiduals(NN_fit_withImport_202212)
#NN_for <- forecast(NN_fit, h=365) 
NN_for_withImport1_202212 <- forecast::forecast(NN_fit_withImport_202212,xreg=ts_import1[99:108],h=9)

NN_for_withImport2_202212 <- forecast::forecast(NN_fit_withImport_202212,xreg=ts_import2[99:108],h=9)

NN_for_withImport3_202212 <- forecast::forecast(NN_fit_withImport_202212,xreg=ts_import3[99:108],h=9)


#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(NN_for_withImport1_202212, series="20%",showgap=F)+
  autolayer(NN_for_withImport2_202212, series="10%",showgap=F)+
  autolayer(NN_for_withImport3_202212, series="5%",PI=FALSE,showgap=F)+
  guides(colour=guide_legend(title="Scenarios (Import Decrease)"))+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
  NN with import as a regressor forecasts a more significant decreasing trend of NG price over 2022, even though at the end of the year, the price is forecasted to be 30 $/MMBtu (similar as previous NN models). The lowest price forecast reaches almost 20 $/MMBtu. There is no significant difference between the three proposed import scenarios.

```{r}
#ETS forecast until 2022.12
ETS_fit2 <-  stlf(ts_EU_price_shorten_201407_202203,h=10)
#checkresiduals(ETS_fit2)

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ETS_fit2, series="STL + ETS",showgap=F) +
  ylab("EU Natural Gas Price ($/MMBtu)")

```
  Because our historical data shows a significant increase since 2021, we expect the forecast in 2022 to have a high uncertainty. This is proved by our second best model: STL_ETS. The forecast results show a overall increasing trend reaching NG price around 60 $/MMBtu until the end of the year. There is also a wide confidence interval ranges from negative NG price value to higher than 150 $/MMBtu.

```{r ARIMA forecast untill 2022.12}
ARIMA_fit_202212<-auto.arima(ts_EU_price_shorten_201407_202203, 
                             seasonal=FALSE, 
                             lambda=0)

ARIMA_for_202212 <- forecast::forecast(ARIMA_fit_202212,h=10)
                           

#Plot model + observed data
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_for_202212,showgap=F)+
  ylab("EU Natural Gas Price ($/MMBtu)") 
```
  To have a sense on how the integration of exogenous variables affect the confidence interval change, we conducted forecast using ARIMA models even though the their RMSE score is not as good as NN or STL+ETS.In contrast to STL+ETS result, the ARIM forecast shows a peak in NG price in the mid 2022, and a drop to around 30 $/MMBtu at the end of the year. However, the confidence interval is still wide with a rnage from 10 to almost 100 $/MMBtu.

```{r ARIMA+GDP Forecast in three scenarios}
ARIMA_Four_fit_withGDP_202212 <- auto.arima(ts_EU_price_shorten_201407_202203, 
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=ts_EU_GDP_201407_202203
                             )
ARIMA_Four_for_withGDP1_202212 <- forecast::forecast(ARIMA_Four_fit_withGDP_202212,
                           xreg=ts_EU_GDP1_202203_202301,
                           h=9
                           ) 
ARIMA_Four_for_withGDP2_202212 <- forecast::forecast(ARIMA_Four_fit_withGDP_202212,
                           xreg=ts_EU_GDP2_202203_202301,
                           h=9
                           ) 
ARIMA_Four_for_withGDP3_202212 <- forecast::forecast(ARIMA_Four_fit_withGDP_202212,
                           xreg=ts_EU_GDP3_202203_202301,
                           h=9
                           ) 
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_Four_for_withGDP1_202212, series="4%",showgap=F) +
  autolayer(ARIMA_Four_for_withGDP2_202212, series="3% ",PI=FALSE,showgap=F) +
  autolayer(ARIMA_Four_for_withGDP3_202212, series="1%",PI=FALSE,showgap=F)+   
  guides(colour=guide_legend(title="Scenarios (GDP Increase)"))+
  ylab("EU Natural Gas Price ($/MMBtu)")
checkresiduals(ARIMA_Four_fit_withGDP_202212)
```
  The ARIMA model with GDP as a regressor shows a similar trend, leading to a slightly lower price forecast at the end of the year (25$/MMbtu) than the original ARIMA model (30$/MMBtu), and the forecast is still with high uncertainaty (i.e. wide confidence interval). There is no significant forecast differences under the three scenarios we proposed, and neither of the three scenarios cause a significant change in the forecast result compared to the original ARIMA model.

```{r ARIMA+Import Forecast with 3 scenarios}
ARIMA_Four_fit_withimport_202212 <- Arima(ts_EU_price_shorten_201407_202203,order=c(0,1,1),include.drift=TRUE,xreg=ts_EU_import_201407_202203
                             )
ARIMA_Four_for_withimport1_202212 <- forecast::forecast(ARIMA_Four_fit_withimport_202212,
                           xreg=ts_EU_import1_201407_202212[93:102],
                           h=9
                           ) 
ARIMA_Four_for_withimport2_202212 <- forecast::forecast(ARIMA_Four_fit_withimport_202212,
                           xreg=ts_EU_import2_201407_202212[93:102],
                           h=9
                           ) 
ARIMA_Four_for_withimport3_202212 <- forecast::forecast(ARIMA_Four_fit_withimport_202212,
                           xreg=ts_EU_import3_201407_202212[93:102],
                           h=9
                           ) 
autoplot(ts_EU_price_shorten_201407_202203) +
  autolayer(ARIMA_Four_for_withimport1_202212, series="20%",showgap=F) +
  autolayer(ARIMA_Four_for_withimport3_202212, series="5%",PI=FALSE,showgap=F) +
  autolayer(ARIMA_Four_for_withimport2_202212, series="10%",PI=FALSE,showgap=F) +
  guides(colour=guide_legend(title="Scenarios (Import Decrease)"))+
  ylab("EU Natural Gas Price ($/MMBtu)")
```
  ARIMA models with import as an regressor shows a completely different resluts than the previous models. THere are mmuch smaller fluctuation and the overall trend is going upward, leading to a NG price forecast at aorund 45 $/MMbtu at the end of 2022.The much narrower confidence interval indicates that the intergration of import data improve the uncertainty of the price forecast. Three import scenarios lead to smilar trend but slightly off level of forecasts. Import decrease by 5% returns the lowest NG price forecast,while import decrease by 20% returns the highest NG price forecast. 